\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-12-08 paper.tex
applied some more fixes by Wouter

The internet of things (IoT) holds great potential to positively influence our
daily work and life through domotics, assisted living, e-health and enhanced
learning \cite{atzori2010internet}. With this potential the IoT also presents a
significant threat: by opening our smart homes and personal data to all of
these interconnected devices, we also open them to everyone who is able to
break the virtual locks that protect them (i.e.\ passwords \& encryption keys).
Implementation of security measures by itself is hindered by the fact that IoT
devices typically have limited batteries, processing power and memory.

@@

Attackers have access to a large set of possible attack vectors
\cite{aschenbruck2012security}, ranging from the physical layer, through the
access and routing layers, up to the application layer. Each layer presents
different opportunities to manipulate data, eavesdrop or perform a form of
denial of service. For each of these attacks an algorithm needs to look for
patterns or anomalies. An IDS for IoT devices therefore requires a large number
of algorithms for an adequate coverage.

@@

Current developments in ID on resource-constrained devices focus on programming
frameworks that structure the implementation of algorithms \cite{valero2012di}
and offer the required basic functional components to implement them
\cite{krontiris2008lidea}. A key shortcoming of prior ID frameworks is that
they don't offer a way to optimize the usage of resources. A solution that
supports the integration of multiple algorithms on IoT devices needs to avoid
accumulating their impact on the available resources. A second omission is
support for systematic reuse to create different configurations. Addressing
this in a transparent and automated way offers the potential to significantly
reduce the effort of developing an IDS.

@@

Relying on basic hardware and software allows us to validate that the generator
is capable of generating code even for the most basic environment. It shows
that the requirements of the generator towards the platform are minimal, don't
rely on advanced frameworks or operating systems, and therefore are applicable
in any environment, targeting any platform.

@@

Section \ref{classification} introduced some ID algorithms
\cite{ganeriwal2008reputation,mishra2004intrusion,krontiris2009cooperative} and
presented a classification
\cite{mishra2004intrusion,ioannis2007towards,alrajeh2013intrusion} based on
their detection approach and interaction style.

This section focuses on related work in the field of domain specific languages
and code generation, both in relation to wireless networks of
resource-constrained devices. These two components are the core of the \NAME
framework and the solution it proposes. We also look at their application in
other disciplines and how this can relate to our context.

>>>>

The internet of things (IoT) holds great potential to positively influence our
daily work and life through domotics, assisted living, e-health, enhanced
learning, etc. \cite{atzori2010internet}. With this potential the IoT also
presents a significant threat: by opening our smart homes and personal data to
all of these interconnected devices, we also open them to everyone who is able
to break the virtual locks that protect them (i.e.\ passwords \& encryption
keys). Implementation of security measures by itself is hindered by the fact
that IoT devices typically have limited batteries, processing power and memory.

@@

Attackers have access to a large set of possible attack vectors
\cite{aschenbruck2012security}, ranging from the physical layer, through the
access and routing layers, up to the application layer. Each layer presents
different opportunities to manipulate data, eavesdrop or perform a form of
denial of service. For each of these attacks an algorithm needs to look for
patterns or anomalies. An IDS for IoT devices therefore requires a large number
of algorithms to achieve adequate coverage.

@@

Current developments in ID on resource-constrained devices focus on programming
frameworks that structure the implementation of algorithms \cite{valero2012di}
and offer the required basic functional components to implement them
\cite{krontiris2008lidea}. A key shortcoming of prior ID frameworks is that
they do not offer a way to optimize the usage of resources. A solution that
supports the integration of multiple algorithms on IoT devices needs to avoid
accumulating their impact on the available resources. A second omission is
support for systematic reuse to create different configurations. Addressing
this in a transparent and automated way offers the potential to significantly
reduce the effort of developing an IDS.

@@

Relying on basic hardware and software allows us to validate that the generator
is capable of generating code even for the most basic environment. It shows
that the requirements of the generator towards the platform are minimal, do not
rely on advanced frameworks or operating systems, and therefore are applicable
in any environment, targeting any platform.

@@

Section \ref{classification} introduced some ID algorithms
\cite{ganeriwal2008reputation,mishra2004intrusion,krontiris2009cooperative} and
presented a classification
\cite{mishra2004intrusion,ioannis2007towards,alrajeh2013intrusion} based on
detection approach and interaction style.

This section focuses on related work in the field of domain specific languages
and code generation, both in relation to wireless networks of
resource-constrained devices. These two components are the core of the \NAME
framework and the solution it proposes. We also look at their application in
other disciplines and analyze how this can relate to our context.
